### 2017-05-23 gpu-04-02-sequential.tex
Move exp. setup into GPU section

In summary, a multitude of localized optimizations were applied to achieve
an efficient sequential baseline version, which is 1000..1500 times faster
than the original Python code, see Section~\ref{sec-evaluation}.
All transformations were rigorously tested to ensure they do
not modify the behavior of the algorithm.

>>>>

In summary, a multitude of localized optimizations were applied to achieve
an efficient sequential baseline version, which is 1000..1500 times faster
than the original Python code, see the next Section.
All transformations were rigorously tested to ensure they do
not modify the behavior of the algorithm.
